Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf = read.csv('pseudo_facebook.tsv', sep = '\t')
str(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)
qplot(data = pf, x = dob_day) + 
  scale_x_continuous(breaks=1:31)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(data = pf, x = dob_day) + 
  scale_x_continuous(breaks=1:31) +
  facet_wrap(~dob_month, ncol = 3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram()
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
# qplot(data = pf, x = friend_count, xlim = c(0, 1000))
qplot(data = pf, x = friend_count) +
  scale_x_continuous(limits = c(0, 1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
# qplot(x = friend_count, data = pf, binwidth = 10) +
#   scale_x_continuous(limits = c(0, 1000),
#                      breaks = seq(0, 1000, 50))
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                    breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender, ncol = 3)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = na.omit(pf), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                    breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender, ncol = 2)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
qplot(x = friend_count, data = na.omit(pf), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                    breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender, ncol = 2)
```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x = tenure/365), data = pf) + 
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x = tenure/365), data = pf) + 
  geom_histogram(binwidth = .25, 
                 color = 'black', 
                 fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure/365), data = pf) + 
  geom_histogram(binwidth = .25, 
                 color = 'black', 
                 fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) +
  xlab('Number of years using Facebook') +
  ylab('Number of users in sample')
```

***

### User Ages
Notes:

```{r User Ages}
ggplot(aes(x = age), data = pf) + 
  geom_histogram(binwidth = 1, 
                 color = 'black', 
                 fill = '#5760AB') +
  scale_x_continuous(breaks = seq(1, 113, 5), limits = c(0, 113)) +
  xlab('Age') +
  ylab('Number of users in sample')
```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
# install.packages('gridExtra')
library(gridExtra) 

# define individual plots
p1 <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 100, 
                 color = 'black', 
                 fill = '#F79420') +
  # scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 4)) +
  xlab('Friend count') +
  ylab('Number of users in sample')
p2 <- ggplot(aes(x = log10(friend_count)), data = pf) + 
  geom_histogram(binwidth = .25, 
                 color = 'black', 
                 fill = '#F79420') +
  # scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) +
  xlab('Friend count(log10)') +
  ylab('Number of users in sample')
p3 <- ggplot(aes(x = sqrt(friend_count)), data = pf) + 
  geom_histogram(binwidth = 2, 
                 color = 'black', 
                 fill = '#F79420') +
  # scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) +
  xlab('Friend count(sqrt)') +
  ylab('Number of users in sample')

# arrange plots in grid
grid.arrange(p1, p2, p3, ncol=3)
```

***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth = 10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('好友数量') + 
  ylab('Percentage of users with that friend count')
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
www_likes_data = subset(pf, !is.na(gender))
ggplot(aes(x = www_likes), data = www_likes_data) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()

by(pf$www_likes, pf$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender, y = friend_count, 
      data = subset(pf, !is.na(gender)), 
      geom = 'boxplot')
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender, y = friend_count, 
      data = subset(pf, !is.na(gender)), 
      geom = 'boxplot', ylim = c(0, 1000))

qplot(x = gender, y = friend_count, 
      data = subset(pf, !is.na(gender)), 
      geom = 'boxplot', ylim = c(0, 1000))

# 注意female的箱形图顶部，在250左右，并且没有“Removed 2949 rows...”的提示
qplot(x = gender, y = friend_count, 
      data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') +
  coord_cartesian(ylim = c(0, 1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y = friend_count, 
      data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') +
  coord_cartesian(ylim = c(0, 250))

by(pf$friend_count, pf$gender, summary)
```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
qplot(x = gender, y = friendships_initiated,
      data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') +
  coord_cartesian(ylim = c(0, 130))

by(pf$friendships_initiated, pf$gender, summary)
```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$mobile_check_in <- NA
pf$mobile_check_in = ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in = factor(pf$mobile_check_in)
summary(pf$mobile_check_in)

sum(pf$mobile_check_in == 1) / length(pf$mobile_check_in)
```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!