单一变量
========================================================

***

### 载入diamonds数据库
注释：
```{r Diamonds Data Set}
data(diamonds)

# 查看有多少条数据
nrow(diamonds)

# 查看属性
names(diamonds)

# 查看属性的结构
str(diamonds)

# 查看color的结构
str(diamonds$color)
```

***

### 价格直方图

```{r Diamonds Plot}
ggplot(aes(x = price), data = diamonds, binwidth = 500) + 
  geom_histogram()
```

***

### 价格分布

```{r Diamonds distribution}
summary(diamonds$price)
```

***

### 钻石数量

```{r Diamonds distribution}
nrow(subset(diamonds, price < 500))
nrow(subset(diamonds, price < 250))
nrow(subset(diamonds, price >= 15000))
```

***

### 廉价钻石

```{r Diamonds price distribution}
ggplot(aes(x = price), 
       data = diamonds) + 
  geom_histogram(binwidth = 10, aes(fill = ..count..)) +
  scale_x_continuous(limits = c(300, 2000), breaks = seq(300, 2000, 100))
```


***

### 切工-价格直方图

```{r Diamonds price by cut histogram}
ggplot(aes(x = price), 
       data = diamonds) + 
  geom_histogram(binwidth = 50, aes(fill = ..count..)) +
  facet_wrap(~cut, ncol = 3)
```

***

### 标尺和多直方图

# In the two last exercises, we looked at
# the distribution for diamonds by cut.

# Run the code below in R Studio to generate
# the histogram as a reminder.

```{r Diamonds price by cut histogram}
qplot(x = price, data = diamonds) + facet_wrap(~cut)
```


# In the last exercise, we looked at the summary statistics
# for diamond price by cut. If we look at the output table, the
# the median and quartiles are reasonably close to each other.


```{r Diamonds price by cut histogram}
by(diamonds$price, diamonds$cut, summary)
```

# This means the distributions should be somewhat similar,
# but the histograms we created don't show that.

# The 'Fair' and 'Good' diamonds appear to have 
# different distributions compared to the better
# cut diamonds. They seem somewhat uniform
# on the left with long tails on the right.

# Let's look in to this more.

# Look up the documentation for facet_wrap in R Studio.
# Then, scroll back up and add a parameter to facet_wrap so that
# the y-axis in the histograms is not fixed. You want the y-axis to
# be different for each histogram.

```{r Diamonds price by cut histogram}
qplot(x = price, data = diamonds, binwidth = 200) + 
  facet_wrap(~cut, scales = 'free')
```


# Create a histogram of price per carat
# and facet it by cut. You can make adjustments
# to the code from the previous exercise to get
# started.

# Adjust the bin width and transform the scale
# of the x-axis using log10.

# Submit your final code when you are ready.


```{r Diamonds price by cut histogram}
ggplot(aes(x = price / carat), 
       data = diamonds) + 
  geom_histogram(binwidth = .01, aes(fill = ..count..)) +
  facet_wrap(~cut, ncol = 3) +
  scale_x_log10()
```


# Investigate the price of diamonds using box plots,
# numerical summaries, and one of the following categorical
# variables: cut, clarity, or color.


```{r Diamonds price by cut histogram}
ggplot(aes(x = cut, y = price),
       data = diamonds) + 
  geom_boxplot()
ggplot(aes(x = clarity, y = price),
       data = diamonds) + 
  geom_boxplot()
ggplot(aes(x = color, y = price),
       data = diamonds) + 
  geom_boxplot()
```


```{r Diamonds price by cut histogram}
summary(subset(diamonds, color == 'D')$price)
summary(subset(diamonds, color == 'J')$price)
IQR(subset(diamonds, color == 'D')$price)
IQR(subset(diamonds, color == 'J')$price)
```


# Investigate the price per carat of diamonds across
# the different colors of diamonds using boxplots.

```{r}
ggplot(aes(x = color, y = price / carat),
       data = diamonds) + 
  geom_boxplot()
```


***

### 克拉

```{r}
ggplot(aes(x = carat),
       data = diamonds) + 
  geom_freqpoly(binwidth = .01) +
  scale_x_continuous(breaks = seq(0, 5, .1), limits = c(0, 3))
```




